\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{array}
\usepackage{longtable}
\usepackage{tcolorbox}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{English Vocabulary Practice}
\rhead{COMPREHENSIVE REVIEW — SET 2}
\cfoot{\thepage}

% Section formatting
\titleformat{\section}
{\Large\bfseries\color{blue!70!black}}
{\thesection}{1em}{}

\titleformat{\subsection}
{\large\bfseries\color{blue!50!black}}
{\thesubsection}{1em}{}

% Custom colors
\definecolor{dragonball}{RGB}{255, 140, 0}
\definecolor{idiomcolor}{RGB}{75, 0, 130}
\definecolor{easygreen}{RGB}{34, 139, 34}
\definecolor{mediumyellow}{RGB}{255, 165, 0}
\definecolor{hardred}{RGB}{178, 34, 34}

% Difficulty box styles
\newtcolorbox{easybox}{colback=green!5!white, colframe=easygreen, title={\textbf{EASY} — Recognition \& Matching}}
\newtcolorbox{mediumbox}{colback=yellow!5!white, colframe=mediumyellow, title={\textbf{MEDIUM} — Application \& Context}}
\newtcolorbox{hardbox}{colback=red!5!white, colframe=hardred, title={\textbf{HARD} — Production \& Analysis}}

\begin{document}

\begin{center}
    {\Huge\bfseries Vocabulary Practice Exercises}\\[0.5cm]
    {\Large Comprehensive Review — Practice Set 2}\\[0.5cm]
    \rule{\textwidth}{0.4pt}\\[0.3cm]
    {\large 16 Words • 12 Exercise Types • Source: Dragon Ball Z}\\[0.2cm]
    \textit{Exercises ordered by difficulty: Easy → Medium → Hard}\\[0.2cm]
    \today
\end{center}

\vspace{0.5cm}

\section*{Vocabulary Overview}

\textit{This practice set covers all NEW vocabulary words from Dragon Ball Z (not included in Practice Set 1).}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{\color{dragonball}Dragon Ball Z (New)} & boggling, sluggish, ambush, lurk, shrewd, defiant, grudge, acquainted, ample, outrageous, divert, ponder, stunt, sucker, ominous, pester \\
\hline
\end{tabularx}
\end{center}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Adjectives} & boggling, sluggish, shrewd, defiant, acquainted, ample, outrageous, ominous \\
\hline
\textbf{Nouns} & ambush, grudge, stunt, sucker \\
\hline
\textbf{Verbs} & lurk, divert, ponder, pester, ambush, stunt, sucker \\
\hline
\end{tabularx}
\end{center}

\vspace{0.5cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Difficulty Progression Guide}\\[0.2cm]
\textcolor{easygreen}{\textbf{EASY (Exercises 1-3):}} Recognition, matching, basic recall\\
\textcolor{mediumyellow}{\textbf{MEDIUM (Exercises 4-8):}} Context application, collocations, comprehension\\
\textcolor{hardred}{\textbf{HARD (Exercises 9-12):}} Production, analysis, creative usage
}}
\end{center}

\newpage

% ============================================================
% EASY SECTION
% ============================================================

\begin{center}
{\Large\textcolor{easygreen}{\textbf{— EASY EXERCISES —}}}\\[0.2cm]
\textit{Recognition \& Matching}
\end{center}

\vspace{0.5cm}

\section{Exercise 1: Definitions — Match the Word}

\textit{Match each definition (1-8) with the correct word from the word bank below.}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank A}\\[0.2cm]
boggling \quad sluggish \quad ambush \quad lurk \quad shrewd \quad defiant \quad grudge \quad acquainted
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[label=\arabic*.]
    \item \underline{\hspace{3cm}} — A feeling of anger or dislike towards somebody because of something bad they have done to you in the past, often lasting a long time.

    \item \underline{\hspace{3cm}} — To wait somewhere secretly, especially because you are going to do something bad or illegal.

    \item \underline{\hspace{3cm}} — Moving, reacting, or working more slowly than normal and in a way that seems lazy; lacking energy or speed.

    \item \underline{\hspace{3cm}} — Openly refusing to obey somebody/something, sometimes in an aggressive way; boldly resisting authority.

    \item \underline{\hspace{3cm}} — Causing great surprise, astonishment, or bewilderment; overwhelming or astounding (often in "mind-boggling").

    \item \underline{\hspace{3cm}} — Clever at understanding and making judgements about a situation; having or showing good judgement.

    \item \underline{\hspace{3cm}} — The act of hiding and waiting for somebody and then making a surprise attack on them.

    \item \underline{\hspace{3cm}} — Familiar with something because you have read, seen, or experienced it; having met someone a few times.
\end{enumerate}

\vspace{1cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank B}\\[0.2cm]
ample \quad outrageous \quad divert \quad ponder \quad stunt \quad sucker \quad ominous \quad pester
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[label=\arabic*., start=9]
    \item \underline{\hspace{3cm}} — To think about something carefully and thoroughly for a period of time; to consider or reflect deeply.

    \item \underline{\hspace{3cm}} — To annoy somebody, especially by asking them something many times; to bother repeatedly.

    \item \underline{\hspace{3cm}} — Suggesting that something bad is going to happen in the future; threatening or menacing.

    \item \underline{\hspace{3cm}} — To make somebody/something change direction; to take attention away from something.

    \item \underline{\hspace{3cm}} — Enough or more than enough; plentiful or generous in quantity, size, or amount.

    \item \underline{\hspace{3cm}} — (Slang) A gullible person easily tricked or cheated; to deceive or trick someone.

    \item \underline{\hspace{3cm}} — An action displaying spectacular skill or daring; OR to prevent the growth or development of something.

    \item \underline{\hspace{3cm}} — Offensive, unacceptable, or shocking; OR very unusual or excessive in a bold way.
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 2: Synonyms \& Antonyms}

\subsection*{Part A: Synonyms}
\textit{Match each word (1-8) with its closest synonym from the options.}

\begin{enumerate}[label=\arabic*.]
    \item \textbf{shrewd}
    \begin{enumerate}[label=\Alph*)]
        \item naive \quad B) astute \quad C) foolish \quad D) careless
    \end{enumerate}

    \item \textbf{sluggish}
    \begin{enumerate}[label=\Alph*)]
        \item energetic \quad B) swift \quad C) lethargic \quad D) active
    \end{enumerate}

    \item \textbf{ample}
    \begin{enumerate}[label=\Alph*)]
        \item scarce \quad B) limited \quad C) abundant \quad D) insufficient
    \end{enumerate}

    \item \textbf{defiant}
    \begin{enumerate}[label=\Alph*)]
        \item obedient \quad B) rebellious \quad C) compliant \quad D) submissive
    \end{enumerate}

    \item \textbf{ponder}
    \begin{enumerate}[label=\Alph*)]
        \item ignore \quad B) contemplate \quad C) forget \quad D) dismiss
    \end{enumerate}

    \item \textbf{ominous}
    \begin{enumerate}[label=\Alph*)]
        \item cheerful \quad B) promising \quad C) threatening \quad D) bright
    \end{enumerate}

    \item \textbf{lurk}
    \begin{enumerate}[label=\Alph*)]
        \item appear \quad B) skulk \quad C) reveal \quad D) emerge
    \end{enumerate}

    \item \textbf{outrageous}
    \begin{enumerate}[label=\Alph*)]
        \item reasonable \quad B) moderate \quad C) scandalous \quad D) acceptable
    \end{enumerate}
\end{enumerate}

\vspace{0.5cm}

\subsection*{Part B: Antonyms}
\textit{Choose the word that is most OPPOSITE in meaning.}

\begin{enumerate}[label=\arabic*., start=9]
    \item \textbf{sluggish}
    \begin{enumerate}[label=\Alph*)]
        \item slow \quad B) brisk \quad C) lazy \quad D) tired
    \end{enumerate}

    \item \textbf{ample}
    \begin{enumerate}[label=\Alph*)]
        \item plentiful \quad B) generous \quad C) scarce \quad D) sufficient
    \end{enumerate}

    \item \textbf{defiant}
    \begin{enumerate}[label=\Alph*)]
        \item rebellious \quad B) bold \quad C) compliant \quad D) aggressive
    \end{enumerate}

    \item \textbf{shrewd}
    \begin{enumerate}[label=\Alph*)]
        \item clever \quad B) wise \quad C) gullible \quad D) smart
    \end{enumerate}

    \item \textbf{ominous}
    \begin{enumerate}[label=\Alph*)]
        \item threatening \quad B) dark \quad C) auspicious \quad D) sinister
    \end{enumerate}

    \item \textbf{acquainted}
    \begin{enumerate}[label=\Alph*)]
        \item familiar \quad B) knowledgeable \quad C) unfamiliar \quad D) experienced
    \end{enumerate}
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 3: Word Forms — Complete the Table}

\textit{Fill in the missing word forms. Some boxes may have "---" if no common form exists.}

\vspace{0.5cm}

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
\textbf{Noun} & \textbf{Verb} & \textbf{Adjective} & \textbf{Adverb} \\
\hline
(1) \underline{\hspace{2cm}} & ponder & ponderable & ponderously \\
\hline
diversion & (2) \underline{\hspace{2cm}} & diverting & divertingly \\
\hline
defiance & defy & (3) \underline{\hspace{2cm}} & defiantly \\
\hline
shrewdness & --- & shrewd & (4) \underline{\hspace{2cm}} \\
\hline
sluggishness & --- & (5) \underline{\hspace{2cm}} & sluggishly \\
\hline
(6) \underline{\hspace{2cm}} & acquaint & acquainted & --- \\
\hline
ambush & (7) \underline{\hspace{2cm}} & ambushed & --- \\
\hline
grudge & grudge & (8) \underline{\hspace{2cm}} & grudgingly \\
\hline
outrage & outrage & (9) \underline{\hspace{2cm}} & outrageously \\
\hline
(10) \underline{\hspace{2cm}} & pester & pestering & --- \\
\hline
\end{tabularx}
\end{center}

\newpage

% ============================================================
% MEDIUM SECTION
% ============================================================

\begin{center}
{\Large\textcolor{mediumyellow}{\textbf{— MEDIUM EXERCISES —}}}\\[0.2cm]
\textit{Application \& Context}
\end{center}

\vspace{0.5cm}

\section{Exercise 4: Fill in the Blanks — Context Sentences}

\textit{Complete each sentence with the most appropriate word from the box. Use each word only once.}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
boggling \quad sluggish \quad ambush \quad lurk \quad shrewd \quad defiant \quad grudge \quad acquainted
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[label=\arabic*.]
    \item The mind-\underline{\hspace{2.5cm}} complexity of quantum physics can overwhelm even the brightest students.

    \item After eating that huge Thanksgiving dinner, I felt heavy and \underline{\hspace{2.5cm}} for hours.

    \item A crocodile was \underline{\hspace{2.5cm}}ing just below the surface, waiting for its prey.

    \item The guerrillas set up an \underline{\hspace{2.5cm}} near the bridge to surprise the enemy convoy.

    \item As a \underline{\hspace{2.5cm}} businesswoman, she always negotiates the best deals for her company.

    \item Despite being punished, the teenager remained \underline{\hspace{2.5cm}} and refused to apologize.

    \item She's held a \underline{\hspace{2.5cm}} against her former friend for over ten years.

    \item The new employees should become fully \underline{\hspace{2.5cm}} with the company's safety procedures.
\end{enumerate}

\vspace{0.5cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
ample \quad outrageous \quad divert \quad ponder \quad stunt \quad sucker \quad ominous \quad pester
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[label=\arabic*., start=9]
    \item I need some time to \underline{\hspace{2.5cm}} over this important decision before giving you an answer.

    \item Please stop \underline{\hspace{2.5cm}}ing me with questions while I'm trying to concentrate!

    \item Dark clouds gathered overhead, creating an \underline{\hspace{2.5cm}} atmosphere before the storm.

    \item The government tried to \underline{\hspace{2.5cm}} public attention away from the scandal.

    \item There is \underline{\hspace{2.5cm}} parking space available at the new shopping center.

    \item The con artist \underline{\hspace{2.5cm}}ed him into investing in a fake business scheme.

    \item Poor nutrition during childhood can \underline{\hspace{2.5cm}} a person's physical development.

    \item These hotel prices are absolutely \underline{\hspace{2.5cm}}! We can't afford to stay here.
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 5: Collocations — Choose the Best Match}

\textit{Select the word that best completes each common collocation.}

\begin{enumerate}[label=\arabic*.]
    \item mind-\underline{\hspace{2cm}}
    \begin{enumerate}[label=\Alph*)]
        \item sluggish \quad B) boggling \quad C) shrewd \quad D) ample
    \end{enumerate}

    \item bear/hold/harbour a \underline{\hspace{2cm}}
    \begin{enumerate}[label=\Alph*)]
        \item grudge \quad B) stunt \quad C) ambush \quad D) sucker
    \end{enumerate}

    \item \underline{\hspace{2cm}} in the shadows
    \begin{enumerate}[label=\Alph*)]
        \item ponder \quad B) divert \quad C) lurk \quad D) pester
    \end{enumerate}

    \item \underline{\hspace{2cm}} somebody's attention
    \begin{enumerate}[label=\Alph*)]
        \item lurk \quad B) divert \quad C) grudge \quad D) ambush
    \end{enumerate}

    \item \underline{\hspace{2cm}} economy/growth/demand
    \begin{enumerate}[label=\Alph*)]
        \item ominous \quad B) defiant \quad C) sluggish \quad D) shrewd
    \end{enumerate}

    \item \underline{\hspace{2cm}} businessman/judge
    \begin{enumerate}[label=\Alph*)]
        \item boggling \quad B) ample \quad C) shrewd \quad D) outrageous
    \end{enumerate}

    \item \underline{\hspace{2cm}} time/space/parking
    \begin{enumerate}[label=\Alph*)]
        \item ample \quad B) ominous \quad C) defiant \quad D) sluggish
    \end{enumerate}

    \item \underline{\hspace{2cm}} prices/behaviour
    \begin{enumerate}[label=\Alph*)]
        \item shrewd \quad B) ample \quad C) outrageous \quad D) acquainted
    \end{enumerate}

    \item \underline{\hspace{2cm}} warning/sign/clouds
    \begin{enumerate}[label=\Alph*)]
        \item boggling \quad B) ominous \quad C) sluggish \quad D) defiant
    \end{enumerate}

    \item death-defying \underline{\hspace{2cm}}
    \begin{enumerate}[label=\Alph*)]
        \item grudge \quad B) ambush \quad C) stunt \quad D) sucker
    \end{enumerate}
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 6: Dragon Ball Z Scene Comprehension}

\textit{Read this dialogue inspired by Dragon Ball Z and answer the questions below.}

\vspace{0.3cm}

\begin{tcolorbox}[colback=orange!5!white, colframe=dragonball, title={\textbf{Scene: The Namek Saga — Vegeta's Warning}}]

\textbf{Setting:} Planet Namek. Vegeta has temporarily allied with Gohan and Krillin against Frieza's forces.

\vspace{0.3cm}

\textbf{VEGETA:} Don't be such \textbf{suckers}. Frieza's men have been \textbf{lurking} around these villages for days. They're planning an \textbf{ambush}.

\textbf{KRILLIN:} How do you know that?

\textbf{VEGETA:} Because I'm not \textbf{sluggish} like you earthlings. I've been watching. Those \textbf{ominous} energy readings from the north? That's Dodoria waiting to strike.

\textbf{GOHAN:} But we gave them the Dragon Ball! Why would they attack us now?

\textbf{VEGETA:} (\textit{laughs}) You really aren't \textbf{acquainted} with how Frieza operates, are you? He holds a \textbf{grudge} against anyone who wastes his time. And those prices he demands for mercy? \textbf{Outrageous}. He takes everything and gives nothing.

\textbf{KRILLIN:} So what do we do?

\textbf{VEGETA:} (\textit{crosses arms, \textbf{defiant}}) We don't run. We \textbf{divert} their attention. Make them think we're heading east while we circle back. I've had \textbf{ample} time to \textbf{ponder} this strategy.

\textbf{GOHAN:} That's actually... \textbf{shrewd}.

\textbf{VEGETA:} Don't act so surprised. Now stop \textbf{pestering} me with questions and move! The mind-\textbf{boggling} power of Frieza's army won't \textbf{stunt} my plans for revenge.

\end{tcolorbox}

\vspace{0.5cm}

\textbf{Questions:}

\begin{enumerate}[label=\arabic*.]
    \item What word does Vegeta use to describe Gohan and Krillin as easily fooled?

    \underline{\hspace{8cm}}

    \item What have Frieza's men been doing around the villages?

    \underline{\hspace{8cm}}

    \item How does Vegeta describe himself compared to the "earthlings"?

    \underline{\hspace{8cm}}

    \item What word describes Frieza's demands for mercy?

    \underline{\hspace{8cm}}

    \item What is Vegeta's plan to escape the ambush?

    \underline{\hspace{8cm}}

    \item Find the word that means Vegeta has thought carefully about the strategy.

    \underline{\hspace{8cm}}

    \item What adjective describes Vegeta's body language when he says "We don't run"?

    \underline{\hspace{8cm}}

    \item What does Gohan call Vegeta's plan, meaning it shows good judgement?

    \underline{\hspace{8cm}}
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 7: Register \& Formality}

\textit{Some vocabulary words are more formal or literary than their common equivalents. Choose the most appropriate word for each context based on formality level.}

\vspace{0.3cm}

\subsection*{Part A: Formal vs. Informal Contexts}

\begin{enumerate}[label=\arabic*.]
    \item \textbf{Business presentation to executives:}

    "I've had sufficient time to \underline{\hspace{2cm}} the quarterly results."
    \begin{enumerate}[label=\Alph*)]
        \item think about \quad B) ponder \quad C) wonder about \quad D) check out
    \end{enumerate}

    \textit{Why?} \hrulefill

    \vspace{0.3cm}

    \item \textbf{Casual text message to a friend:}

    "Dude, you totally got \underline{\hspace{2cm}} by that salesman lol"
    \begin{enumerate}[label=\Alph*)]
        \item deceived \quad B) suckered \quad C) beguiled \quad D) misled
    \end{enumerate}

    \textit{Why?} \hrulefill

    \vspace{0.3cm}

    \item \textbf{Academic essay on economics:}

    "The \underline{\hspace{2cm}} growth in Q3 suggests underlying structural issues."
    \begin{enumerate}[label=\Alph*)]
        \item slow \quad B) lazy \quad C) sluggish \quad D) tired
    \end{enumerate}

    \textit{Why?} \hrulefill

    \vspace{0.3cm}

    \item \textbf{Fantasy novel narration:}

    "Dark forces \underline{\hspace{2cm}} in the shadows of the ancient fortress."
    \begin{enumerate}[label=\Alph*)]
        \item waited \quad B) hid \quad C) lurked \quad D) stayed
    \end{enumerate}

    \textit{Why?} \hrulefill
\end{enumerate}

\vspace{0.5cm}

\subsection*{Part B: Word Pairs — When to Use Each}

\textit{Explain the difference in register/usage between these pairs:}

\begin{enumerate}[label=\arabic*., start=5]
    \item \textbf{ponder} vs. \textbf{think about}

    \hrulefill

    \hrulefill

    \item \textbf{ample} vs. \textbf{enough}

    \hrulefill

    \hrulefill

    \item \textbf{defiant} vs. \textbf{stubborn}

    \hrulefill

    \hrulefill

    \item \textbf{ominous} vs. \textbf{scary}

    \hrulefill

    \hrulefill
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 8: Listening Comprehension Prompts}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!50!black, title={\textbf{Instructions for Listening Practice}}]
\textbf{Option A:} Have a partner, teacher, or language exchange buddy read these sentences aloud. Write down the vocabulary word you hear.

\textbf{Option B:} Use a text-to-speech tool (Google Translate, Natural Reader, etc.) to hear the sentences and practice identifying words by ear.

\textbf{Option C:} Record yourself reading these sentences, then listen back after a few days and test your recall.
\end{tcolorbox}

\vspace{0.5cm}

\subsection*{Part A: Single Word Identification}
\textit{Listen and write the vocabulary word you hear in each sentence.}

\begin{enumerate}[label=\arabic*.]
    \item "The complexity of the human brain is absolutely mind-\_\_\_\_\_\_\_\_\_\_."

    \item "Someone was \_\_\_\_\_\_\_\_\_\_ in the alley behind the restaurant."

    \item "She's been holding a \_\_\_\_\_\_\_\_\_\_ against him since high school."

    \item "The economy has been quite \_\_\_\_\_\_\_\_\_\_ this quarter."

    \item "He made a \_\_\_\_\_\_\_\_\_\_ investment decision that paid off."

    \item "There's \_\_\_\_\_\_\_\_\_\_ evidence to support the theory."

    \item "The sky looked \_\_\_\_\_\_\_\_\_\_ before the hurricane hit."

    \item "She remained \_\_\_\_\_\_\_\_\_\_ despite the pressure to conform."
\end{enumerate}

\vspace{0.5cm}

\subsection*{Part B: Dictation Practice}
\textit{Listen to these full sentences and write them down. Then check your spelling of the vocabulary words.}

\begin{enumerate}[label=\arabic*., start=9]
    \item \hrulefill

    \hrulefill

    (\textit{Answer: "The guerrillas ambushed the convoy near the mountain pass."})

    \item \hrulefill

    \hrulefill

    (\textit{Answer: "I need more time to ponder this difficult decision."})

    \item \hrulefill

    \hrulefill

    (\textit{Answer: "Don't let them sucker you into buying unnecessary insurance."})

    \item \hrulefill

    \hrulefill

    (\textit{Answer: "Are you acquainted with the new safety regulations?"})
\end{enumerate}

\newpage

% ============================================================
% HARD SECTION
% ============================================================

\begin{center}
{\Large\textcolor{hardred}{\textbf{— HARD EXERCISES —}}}\\[0.2cm]
\textit{Production \& Analysis}
\end{center}

\vspace{0.5cm}

\section{Exercise 9: Trap Sentences — Spot the Misuse}

\begin{tcolorbox}[colback=red!5!white, colframe=hardred]
\textbf{Warning:} These sentences contain vocabulary words that \textit{almost} fit but are used incorrectly. Your job is to identify WHY the word doesn't work and suggest a better alternative.
\end{tcolorbox}

\vspace{0.5cm}

\textit{Each sentence contains a misused vocabulary word. Explain the error and provide a correction.}

\begin{enumerate}[label=\arabic*.]
    \item "I need to \textbf{ponder} quickly about what to order for lunch."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "The cheerful music created an \textbf{ominous} atmosphere at the birthday party."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "After drinking three cups of coffee, I felt very \textbf{sluggish} and energetic."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "She \textbf{lurked} openly in the middle of the crowded plaza."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "He made a \textbf{shrewd} decision by investing all his money in a random cryptocurrency without research."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "The obedient student was very \textbf{defiant} and always followed the rules."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "We had \textbf{ample} time—only 30 seconds to complete the entire exam."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill

    \vspace{0.3cm}

    \item "The soldiers launched a surprise \textbf{ambush} by marching openly down the main road in broad daylight."

    \textbf{Error:} \hrulefill

    \textbf{Why it's wrong:} \hrulefill

    \textbf{Better word:} \hrulefill
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 10: Error Correction}

\textit{Each sentence contains ONE grammatical error related to vocabulary usage. Find and correct it.}

\begin{enumerate}[label=\arabic*.]
    \item After the big lunch, I felt very \textbf{sluggishly} and needed a nap.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item She has been \textbf{lurked} in the online forum for months without posting anything.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item The teenager gave her parents a \textbf{defiantly} look and stormed out of the room.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item He's been holding a \textbf{grudging} against his former business partner for years.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item The employees should become \textbf{acquaint} with the new safety regulations.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item We had \textbf{amply} time to finish the project before the deadline.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item The guerrillas \textbf{ambushed on} the convoy near the mountain pass.

    \underline{Correction:} \hrulefill

    \vspace{0.3cm}

    \item She needs more time to \textbf{pondering} over the important decision.

    \underline{Correction:} \hrulefill
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 11: Translation \& Production}

\subsection*{Part A: English to Portuguese}
\textit{Translate the following sentences into Portuguese, paying attention to the underlined vocabulary.}

\begin{enumerate}[label=\arabic*.]
    \item The \underline{mind-boggling} complexity of the universe continues to amaze scientists.

    \vspace{1cm}

    \item She has \underline{harboured a grudge} against him for years after their argument.

    \vspace{1cm}

    \item The \underline{ominous} clouds suggested a terrible storm was approaching.

    \vspace{1cm}

    \item He was too \underline{shrewd} to be taken in by their deceptive sales pitch.

    \vspace{1cm}

    \item The government tried to \underline{divert} public attention from the scandal.

    \vspace{1cm}
\end{enumerate}

\subsection*{Part B: Portuguese to English}
\textit{Translate the following sentences into English using the vocabulary from this set.}

\begin{enumerate}[label=\arabic*., start=6]
    \item Ele se sentiu muito lerdo e pesado após a refeição. (Use: sluggish)

    \vspace{1cm}

    \item Os guerrilheiros os emboscaram perto da ponte. (Use: ambush)

    \vspace{1cm}

    \item Eu não a conheço pessoalmente. (Use: acquainted)

    \vspace{1cm}

    \item Há estacionamento gratuito amplo disponível. (Use: ample)

    \vspace{1cm}

    \item Alguém estava à espreita nas sombras. (Use: lurk)

    \vspace{1cm}
\end{enumerate}

\subsection*{Part C: Sentence Creation}
\textit{Write original sentences using each word correctly. Include context that demonstrates understanding.}

\begin{enumerate}[label=\arabic*., start=11]
    \item \textbf{pester}:

    \vspace{1cm}

    \item \textbf{defiant}:

    \vspace{1cm}

    \item \textbf{sucker (verb)}:

    \vspace{1cm}

    \item \textbf{stunt (noun)}:

    \vspace{1cm}

    \item \textbf{outrageous}:

    \vspace{1cm}
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 12: Advanced Reading \& Analysis}

\textit{Read the passage and answer the analytical questions.}

\vspace{0.3cm}

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!50!black, title={\textbf{The Failed Business Deal}}]

Marcus had always considered himself a \textbf{shrewd} investor, but this time he had been \textbf{suckered} into a terrible deal. The investment opportunity had seemed too good to be true—and it was.

The con artists had been \textbf{lurking} in the financial district for months, waiting for wealthy victims. When they approached Marcus, they \textbf{diverted} his attention from the obvious red flags by showing him impressive (but fake) financial reports.

At first, Marcus took \textbf{ample} time to \textbf{ponder} the decision. However, the salespeople began to \textbf{pester} him with daily calls, creating a false sense of urgency. The promised returns were so \textbf{outrageous}—300\% profit in just six months—that anyone less greedy would have been suspicious.

When the truth emerged, Marcus felt \textbf{sluggish} and depressed for weeks. The financial loss was \textbf{mind-boggling}—over two million dollars gone. Dark, \textbf{ominous} thoughts clouded his mind.

His wife still held a \textbf{grudge} against the people who had ruined them, while their teenage daughter remained \textbf{defiant}, insisting the family would recover. Marcus wasn't so sure. Though \textbf{acquainted} with failure from his early business days, nothing had prepared him for this.
\end{tcolorbox}

\vspace{0.5cm}

\textbf{Analytical Questions:}

\begin{enumerate}[label=\arabic*.]
    \item How does the author create irony with the word "shrewd" in the opening sentence?

    \vspace{1.2cm}

    \item The passage uses "lurking" to describe the con artists. What connotation does this create, and how does it foreshadow the outcome?

    \vspace{1.2cm}

    \item Identify TWO vocabulary words that describe Marcus's emotional/physical state after the scam. How do they reinforce the theme of loss?

    \vspace{1.2cm}

    \item Compare the reactions of Marcus, his wife, and his daughter. Which vocabulary words characterize each person's response?

    \vspace{1.2cm}

    \item The word "outrageous" is used to describe the promised returns. Is this usage positive or negative in context? Explain.

    \vspace{1.2cm}
\end{enumerate}

\newpage

% ============================================================
% QUICK REFERENCE PAGE
% ============================================================

\section*{Quick Reference — Vocabulary Set 2}

\begin{center}
\rule{\textwidth}{0.4pt}\\[0.3cm]
{\Large\textbf{16 Words at a Glance}}\\[0.2cm]
\textit{Tear out or bookmark this page for quick review}
\end{center}

\vspace{0.5cm}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{longtable}{|p{2.5cm}|p{2cm}|p{6cm}|p{3.5cm}|}
\hline
\textbf{Word} & \textbf{Type} & \textbf{Definition} & \textbf{Portuguese} \\
\hline
\endfirsthead
\hline
\textbf{Word} & \textbf{Type} & \textbf{Definition} & \textbf{Portuguese} \\
\hline
\endhead

acquainted & adj & Familiar with; having met someone & familiarizado \\
\hline
ambush & n/v & Surprise attack from hiding; to attack by surprise & emboscada; emboscar \\
\hline
ample & adj & Enough or more than enough; plentiful & amplo, abundante \\
\hline
boggling & adj & Causing astonishment (mind-boggling) & espantoso, alucinante \\
\hline
defiant & adj & Openly refusing to obey; rebellious & desafiante, rebelde \\
\hline
divert & v & To change direction; to distract attention & desviar, distrair \\
\hline
grudge & n & Long-lasting feeling of anger/resentment & rancor, mágoa \\
\hline
lurk & v & To wait secretly, often with bad intent & espreitar, merodear \\
\hline
ominous & adj & Suggesting something bad will happen & ameaçador, sinistro \\
\hline
outrageous & adj & Shocking, offensive; OR excessively bold & ultrajante, exorbitante \\
\hline
pester & v & To annoy by asking repeatedly & importunar, chatear \\
\hline
ponder & v & To think carefully and deeply & ponderar, refletir \\
\hline
shrewd & adj & Clever at judgement; astute & astuto, sagaz \\
\hline
sluggish & adj & Moving slowly; lacking energy & lento, lerdo \\
\hline
stunt & n/v & Daring action; OR to prevent growth & façanha; inibir \\
\hline
sucker & n/v & Gullible person; to trick someone & otário; enganar \\
\hline

\end{longtable}
\end{center}

\vspace{0.5cm}

\subsection*{Key Collocations to Remember}

\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
    \item mind-\textbf{boggling}
    \item \textbf{sluggish} economy/growth
    \item \textbf{lurk} in the shadows
    \item \textbf{shrewd} businessman
    \item \textbf{defiant} attitude
    \item hold/bear a \textbf{grudge}
    \item \textbf{ample} time/space
    \item \textbf{outrageous} prices
    \item \textbf{ominous} clouds/warning
    \item \textbf{divert} attention
    \item death-defying \textbf{stunt}
    \item get \textbf{suckered} into
    \item become \textbf{acquainted} with
    \item \textbf{ponder} a decision
    \item \textbf{pester} someone with questions
    \item set up an \textbf{ambush}
\end{itemize}
\end{multicols}

\vspace{1cm}

\begin{center}
\rule{0.8\textwidth}{0.4pt}\\[0.3cm]
{\Large\textbf{End of Exercises}}\\[0.2cm]
{\textit{Check your answers with the answer key}}
\end{center}

\end{document}
