\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{array}
\usepackage{longtable}
\usepackage{tcolorbox}
\usepackage{soul}
\usepackage{dashrule}
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{pifont}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{English Vocabulary Practice}
\rhead{COMPREHENSIVE REVIEW — SET 3}
\cfoot{\thepage}

% Section formatting
\titleformat{\section}
{\Large\bfseries\color{blue!70!black}}
{\thesection}{1em}{}

\titleformat{\subsection}
{\large\bfseries\color{blue!50!black}}
{\thesubsection}{1em}{}

% Custom colors
\definecolor{dragonball}{RGB}{255, 140, 0}
\definecolor{idiomcolor}{RGB}{75, 0, 130}
\definecolor{easygreen}{RGB}{34, 139, 34}
\definecolor{mediumyellow}{RGB}{255, 165, 0}
\definecolor{hardred}{RGB}{178, 34, 34}
\definecolor{reviewpurple}{RGB}{128, 0, 128}
\definecolor{lightgray}{gray}{0.9}

% Difficulty box styles
\newtcolorbox{easybox}{colback=green!5!white, colframe=easygreen, title={\textbf{EASY} — Recognition \& Matching}}
\newtcolorbox{mediumbox}{colback=yellow!5!white, colframe=mediumyellow, title={\textbf{MEDIUM} — Application \& Context}}
\newtcolorbox{hardbox}{colback=red!5!white, colframe=hardred, title={\textbf{HARD} — Production \& Analysis}}

% Dialogue box style
\newtcolorbox{dialoguebox}[1][]{
    colback=orange!5!white,
    colframe=dragonball,
    fonttitle=\bfseries,
    title=#1
}

% Review box style (for spaced repetition words)
\newtcolorbox{reviewbox}{
    colback=purple!5!white,
    colframe=reviewpurple,
    title={\textbf{SPACED REPETITION --- Words from Previous Sets}}
}

\begin{document}

% ============================================================
% MAIN DOCUMENT STARTS
% ============================================================

\begin{center}
    {\Huge\bfseries Vocabulary Practice Exercises}\\[0.5cm]
    {\Large Comprehensive Review — Practice Set 3}\\[0.5cm]
    \rule{\textwidth}{0.4pt}\\[0.3cm]
    {\large 40 New Words + 5 Review Words • 14 Exercise Types • Source: Dragon Ball Z}\\[0.2cm]
    \textit{Exercises ordered by difficulty: Easy → Medium → Hard}\\[0.2cm]
    \today\\[0.4cm]
    \fbox{\parbox{0.7\textwidth}{\centering \textbf{Quick Reference table with all words is at the end of this document}}}
\end{center}

\vspace{0.5cm}

\section*{Vocabulary Overview}

\textit{This practice set covers all NEW vocabulary words from Dragon Ball Z added since Practice Set 2, plus 5 review words from previous sets for spaced repetition.}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{\color{dragonball}DBZ (New)} & sicken, insidious, ensued, diaper, wayside, brazen, ruffled, dizzy, preposterous, hasten, loom, tossed, dicey, foreboding, mischievous, seized, canopy, sass, halt, nuisance, uncanny, grievous, grin, savory, fiendish, unquenchable, thereby, cunning, lucky break, bustling, uptight, eager, threshold, grip, fierce, scatter, hideous, safe and sound, scum, twisted mind \\
\hline
\textbf{\color{reviewpurple}Review Words} & jeopardize, withstand, meddling, ominous, shrewd \\
\hline
\end{tabularx}
\end{center}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Adjectives} & insidious, brazen, ruffled, dizzy, preposterous, dicey, mischievous, uncanny, grievous, savory, fiendish, unquenchable, cunning, bustling, uptight, eager, fierce, hideous \\
\hline
\textbf{Nouns} & diaper, wayside, foreboding, canopy, sass, nuisance, grin, threshold, grip, scum \\
\hline
\textbf{Verbs} & sicken, ensue, hasten, loom, toss, seize, halt, scatter, grip \\
\hline
\textbf{Adverbs} & thereby \\
\hline
\textbf{Idioms/Expressions} & fall by the wayside, safe and sound, lucky break, twisted mind \\
\hline
\end{tabularx}
\end{center}

\vspace{0.5cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Difficulty Progression Guide}\\[0.2cm]
\textcolor{easygreen}{\textbf{EASY (Exercises 1-4):}} Recognition, matching, basic recall\\
\textcolor{mediumyellow}{\textbf{MEDIUM (Exercises 5-9):}} Context application, collocations, comprehension\\
\textcolor{hardred}{\textbf{HARD (Exercises 10-14):}} Production, analysis, creative usage
}}
\end{center}

\newpage

% ============================================================
% EASY SECTION
% ============================================================

\begin{center}
\begin{tcolorbox}[colback=green!5!white, colframe=easygreen, width=0.95\textwidth, arc=3mm, boxrule=1.5pt]
\begin{center}
{\Large\textbf{--- EASY EXERCISES ---}}\\[0.2cm]
{\large\textit{Recognition \& Matching}}\\[0.3cm]
\textbf{Exercises 1-4} focus on recognition and basic recall. If you can complete these quickly with 90\%+ accuracy, you're ready to move on to Medium exercises.
\end{center}
\end{tcolorbox}
\end{center}

\vspace{0.5cm}

\section{Definitions Matching}
\textit{Match each word (1-20) with its correct definition (A-T). Write the letter on the line provided.}

\begin{multicols}{2}
\begin{enumerate}
    \item sicken \rule{1cm}{0.4pt}
    \item insidious \rule{1cm}{0.4pt}
    \item ensued \rule{1cm}{0.4pt}
    \item brazen \rule{1cm}{0.4pt}
    \item preposterous \rule{1cm}{0.4pt}
    \item hasten \rule{1cm}{0.4pt}
    \item loom \rule{1cm}{0.4pt}
    \item foreboding \rule{1cm}{0.4pt}
    \item mischievous \rule{1cm}{0.4pt}
    \item cunning \rule{1cm}{0.4pt}
    \item uncanny \rule{1cm}{0.4pt}
    \item grievous \rule{1cm}{0.4pt}
    \item fiendish \rule{1cm}{0.4pt}
    \item unquenchable \rule{1cm}{0.4pt}
    \item bustling \rule{1cm}{0.4pt}
    \item threshold \rule{1cm}{0.4pt}
    \item fierce \rule{1cm}{0.4pt}
    \item hideous \rule{1cm}{0.4pt}
    \item thereby \rule{1cm}{0.4pt}
    \item nuisance \rule{1cm}{0.4pt}
\end{enumerate}
\end{multicols}

\begin{multicols}{2}
\begin{enumerate}[label=\Alph*.]
    \item Happened next, as a result
    \item Full of busy activity
    \item Shamelessly bold, without guilt
    \item A feeling that something bad will happen
    \item To hurry; to speed something up
    \item To disgust; cause shock and anger
    \item Spreading harm gradually, unnoticed
    \item By that means; as a result
    \item Playfully naughty
    \item Strangely mysterious; eerily accurate
    \item A doorway; the starting point or limit
    \item An annoying person or thing
    \item Aggressively intense; violent
    \item Cleverly deceitful; crafty
    \item Extremely cruel; devilishly difficult
    \item Impossible to satisfy
    \item Very serious (harm, error, injustice)
    \item Extremely ugly; horrifying
    \item Absurdly ridiculous
    \item To appear threatening; seem imminent
\end{enumerate}
\end{multicols}

\vspace{0.5cm}

\section{Synonyms \& Antonyms}
\textit{For each word, write ONE synonym and ONE antonym from the word banks provided.}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{SYNONYMS Word Bank}\\[0.2cm]
crafty \quad calm \quad disgusting \quad dangerous \quad eerie \quad grab \quad throw \quad serious \quad scatter \quad rush \quad satisfied \quad stop \quad absurd \quad cruel \quad lively \quad bold \quad pleasant
}}
\end{center}

\vspace{0.5cm}

\begin{tabularx}{\textwidth}{|p{3.5cm}|X|X|}
\hline
\textbf{Word} & \textbf{Synonym} & \textbf{Antonym} \\
\hline
1. fierce (adj.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
2. cunning (adj.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
3. hideous (adj.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
4. halt (v.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
5. hasten (v.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
6. seized (v.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
7. dicey (adj.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
8. uncanny (adj.) & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} & \parbox[t][0.6cm][t]{\linewidth}{\vspace{0.45cm}\hrulefill} \\
\hline
\end{tabularx}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{ANTONYMS Word Bank}\\[0.2cm]
honest \quad gentle \quad beautiful \quad continue \quad delay \quad release \quad safe \quad ordinary \quad satisfiable \quad pleasant \quad calm
}}
\end{center}

\vspace{0.3cm}

\newpage

\section{Word Forms Table}
\textit{Complete the table with the correct word forms. Some cells may be left blank (use "—") if no common form exists.}

\vspace{0.3cm}

\begin{tabularx}{\textwidth}{|l|X|X|X|X|}
\hline
\textbf{Base Word} & \textbf{Noun} & \textbf{Verb} & \textbf{Adjective} & \textbf{Adverb} \\
\hline
sicken & — & sicken & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & sickeningly \\
\hline
grip & grip & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & gripping & — \\
\hline
fierce & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & — & fierce & fiercely \\
\hline
cunning & cunning & — & cunning & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} \\
\hline
eager & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & — & eager & eagerly \\
\hline
scatter & scatter & scatter & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & — \\
\hline
hasten & haste & hasten & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & hastily \\
\hline
foreboding & foreboding & forebode & foreboding & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} \\
\hline
mischievous & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} & — & mischievous & mischievously \\
\hline
grievous & grievance & grieve & grievous & \parbox[t][0.5cm][t]{\linewidth}{\vspace{0.35cm}\rule{2cm}{0.4pt}} \\
\hline
\end{tabularx}

\vspace{0.5cm}

\section{Quick Recall: Fill the Gaps}
\textit{Complete each sentence with the most appropriate word from the box. Use each word only once.}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank}\\[0.2cm]
diaper \quad canopy \quad grin \quad threshold \quad wayside \quad sass \quad scum \quad savory \quad ruffled \quad dizzy
}}
\end{center}

\vspace{0.3cm}

\begin{enumerate}
    \item The baby needs a fresh \rule{3cm}{0.4pt} — the old one is wet.
    
    \item She couldn't hide her wide \rule{3cm}{0.4pt} when she heard the good news.
    
    \item Many ambitious projects have fallen by the \rule{3cm}{0.4pt} due to budget cuts.
    
    \item "Don't give me any of your \rule{3cm}{0.4pt}!" the teacher warned sternly.
    
    \item I prefer \rule{3cm}{0.4pt} snacks like cheese and crackers over sweet desserts.
    
    \item The monkey swung through the forest \rule{3cm}{0.4pt}, high above the ground.
    
    \item Drug dealers are the \rule{3cm}{0.4pt} of the earth.
    
    \item She stood nervously on the \rule{3cm}{0.4pt} of the door, hesitant to enter.
    
    \item His feathers were all \rule{3cm}{0.4pt} after the wind blew through his cage.
    
    \item I felt \rule{3cm}{0.4pt} after spinning around too many times.
\end{enumerate}

\newpage

% ============================================================
% MEDIUM SECTION
% ============================================================

\begin{center}
\begin{tcolorbox}[colback=yellow!5!white, colframe=mediumyellow, width=0.95\textwidth, arc=3mm, boxrule=1.5pt]
\begin{center}
{\Large\textbf{--- MEDIUM EXERCISES ---}}\\[0.2cm]
{\large\textit{Application \& Context}}\\[0.3cm]
\textbf{Exercises 5-9} require applying vocabulary in context. Focus on collocations,\\common usage patterns, and comprehension.
\end{center}
\end{tcolorbox}
\end{center}

\vspace{0.5cm}

\section{Collocations Challenge}
\textit{Choose the word that BEST completes each collocation. Circle your answer.}

\vspace{0.3cm}

\begin{enumerate}
    \item \rule{2cm}{0.4pt} bodily harm (serious physical injury, legal term)
    \begin{enumerate}[label=\alph*)]
        \item grievous
        \item dicey
        \item fierce
        \item hideous
    \end{enumerate}
    
    \item come to a grinding \rule{2cm}{0.4pt}
    \begin{enumerate}[label=\alph*)]
        \item threshold
        \item halt
        \item grip
        \item scatter
    \end{enumerate}
    
    \item \rule{2cm}{0.4pt} resemblance (strangely accurate similarity)
    \begin{enumerate}[label=\alph*)]
        \item cunning
        \item fierce
        \item uncanny
        \item brazen
    \end{enumerate}
    
    \item have a low pain \rule{2cm}{0.4pt}
    \begin{enumerate}[label=\alph*)]
        \item wayside
        \item threshold
        \item canopy
        \item grip
    \end{enumerate}
    
    \item get a \rule{2cm}{0.4pt} break (unexpected lucky chance)
    \begin{enumerate}[label=\alph*)]
        \item dicey
        \item lucky
        \item bustling
        \item fierce
    \end{enumerate}
    
    \item \rule{2cm}{0.4pt} thirst for knowledge (impossible to satisfy)
    \begin{enumerate}[label=\alph*)]
        \item eager
        \item fiendish
        \item unquenchable
        \item cunning
    \end{enumerate}
    
    \item \rule{2cm}{0.4pt} it out (face difficulty with shameless confidence)
    \begin{enumerate}[label=\alph*)]
        \item hasten
        \item brazen
        \item scatter
        \item grip
    \end{enumerate}
    
    \item a \rule{2cm}{0.4pt} feeling that something was wrong
    \begin{enumerate}[label=\alph*)]
        \item dizzy
        \item bustling
        \item foreboding
        \item savory
    \end{enumerate}
    
    \item a crisis was \rule{2cm}{0.4pt} on the horizon
    \begin{enumerate}[label=\alph*)]
        \item scattering
        \item looming
        \item ensuing
        \item gripping
    \end{enumerate}
    
    \item \rule{2cm}{0.4pt} reducing the risk of heart attack (by that means)
    \begin{enumerate}[label=\alph*)]
        \item therefore
        \item thereby
        \item although
        \item furthermore
    \end{enumerate}
\end{enumerate}

\newpage

\section{Media Dialogue Comprehension}
\textit{Read the following Dragon Ball Z scene and answer the questions below.}

\begin{dialoguebox}[Scene: Cell Games Arena — The Z Fighters Face Perfect Cell]
\small

\textbf{NARRATOR:} The situation looked \textbf{dicey} for the Z Fighters. Perfect Cell stood tall, his power \textbf{looming} over them like a dark cloud. A sense of \textbf{foreboding} filled the air as everyone realized just how outmatched they truly were.

\vspace{0.15cm}

\textbf{VEGETA:} [with a \textbf{mischievous} \textbf{grin}] You think you're so powerful, Cell? Your \textbf{brazen} confidence will be your downfall!

\vspace{0.15cm}

\textbf{CELL:} [laughs] Your words don't \textbf{sicken} me, Vegeta. I find your defiance... amusing. But let me \textbf{hasten} to add—your pathetic attacks are merely a \textbf{nuisance}. They cannot even begin to \textbf{jeopardize} my plans.

\vspace{0.15cm}

\textbf{PICCOLO:} [thinking] Cell has an \textbf{uncanny} ability to predict our every move. His power is \textbf{fiendish}—truly, he has a \textbf{twisted mind}. We need to find a way to \textbf{halt} him before more \textbf{grievous} harm comes to the Earth.

\vspace{0.15cm}

\textbf{GOKU:} [stepping forward] Everyone, \textbf{scatter}! Don't let him \textbf{seize} the advantage! Gohan, remember—you have an \textbf{unquenchable} spirit within you. Trust in your power!

\vspace{0.15cm}

\textbf{GOHAN:} [nervously] But Father, I feel so \textbf{uptight}... I'm not sure I can \textbf{withstand} his attacks.

\vspace{0.15cm}

\textbf{GOKU:} [placing his hand on Gohan's shoulder] You're standing on the \textbf{threshold} of greatness, son. This is your moment. Keep a firm \textbf{grip} on your courage, and don't let fear \textbf{scatter} your focus. The Earth is \textbf{eager} for a hero.

\vspace{0.15cm}

\textbf{CELL:} [impatiently] Enough of this \textbf{meddling}! Chaos \textbf{ensued} the last time warriors tried to challenge me, and it will happen again. Your \textbf{shrewd} tactics won't save you. I am \textbf{cunning}, I am perfect, and soon you will all fall by the \textbf{wayside}!

\vspace{0.15cm}

\textbf{NARRATOR:} And so the \textbf{fierce} battle began, the \textbf{bustling} energy of combat filling the arena. Would the Z Fighters emerge \textbf{safe and sound}, or would Cell prove that their efforts were utterly \textbf{preposterous}? Only time would tell...
\end{dialoguebox}

\vspace{0.3cm}

\textbf{Comprehension Questions:}

\begin{enumerate}
    \item What word describes the risky, uncertain situation facing the Z Fighters?
    
    \rule{\textwidth}{0.4pt}
    
    \item Which TWO words describe Cell's cruel intelligence and disturbed thinking?
    
    \rule{\textwidth}{0.4pt}
    
    \item What does Goku tell Gohan he's standing on the edge of?
    
    \rule{\textwidth}{0.4pt}
    
    \item What idiom does Cell use to predict the fighters will fail or be abandoned?
    
    \rule{\textwidth}{0.4pt}
    
    \item Find THREE words in the dialogue that describe negative feelings or situations related to danger/threat.
    
    \rule{\textwidth}{0.4pt}
\end{enumerate}

\newpage

\section{Register \& Formality Awareness}
\textit{Understanding when to use formal vs. informal language is crucial for natural English.}

\vspace{0.3cm}

\subsection*{Part A: Choose the more formal option}
\textit{For each pair of sentences, identify which one is MORE FORMAL. Then, identify the vocabulary word that signals the register.}

\vspace{0.3cm}

\begin{enumerate}
    \item \textbf{Pair A:}
    \begin{enumerate}[label=(\roman*)]
        \item The meeting was called off, thereby delaying the project by two weeks.
        \item The meeting was called off, so the project got pushed back two weeks.
    \end{enumerate}
    More formal: \rule{1cm}{0.4pt} \quad Key word: \rule{3cm}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \textbf{Pair B:}
    \begin{enumerate}[label=(\roman*)]
        \item She hastened to explain her actions to the committee.
        \item She quickly tried to explain her actions to the committee.
    \end{enumerate}
    More formal: \rule{1cm}{0.4pt} \quad Key word: \rule{3cm}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \textbf{Pair C:}
    \begin{enumerate}[label=(\roman*)]
        \item The defendant was charged with causing grievous bodily harm.
        \item The defendant was charged with seriously hurting someone.
    \end{enumerate}
    More formal: \rule{1cm}{0.4pt} \quad Key word: \rule{3cm}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \textbf{Pair D:}
    \begin{enumerate}[label=(\roman*)]
        \item The whole situation seems pretty dicey to me.
        \item The circumstances appear rather precarious.
    \end{enumerate}
    More formal: \rule{1cm}{0.4pt} \quad Informal word from Set 3: \rule{3cm}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \textbf{Pair E:}
    \begin{enumerate}[label=(\roman*)]
        \item He has an insidious influence on the organization's culture.
        \item He's been a bad influence on how things work around here.
    \end{enumerate}
    More formal: \rule{1cm}{0.4pt} \quad Key word: \rule{3cm}{0.4pt}
\end{enumerate}

\newpage

\section{Listening Comprehension}
\textit{This exercise simulates listening to spoken English. Read aloud or have someone read to you.}

\subsection*{Part A: Sentence Dictation}
\textit{Have someone read each sentence aloud while you write what you hear. Then check your spelling.}

\vspace{0.1cm}

\textbf{Note:} The sentences to read aloud are in the Answer Key.

\vspace{0.3cm}

\begin{enumerate}
    \item \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.3cm}
    
    \item \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
\end{enumerate}

\subsection*{Part B: Word Recognition}
\textit{Listen to the audio descriptions (have someone read them) and write which Set 3 vocabulary word is being described.}

\vspace{0.1cm}

\textbf{Note:} The descriptions to read aloud are in the Answer Key.

\vspace{0.3cm}

\begin{enumerate}
    \item Word: \rule{6cm}{0.4pt}
    
    \vspace{0.8cm}
    
    \item Word: \rule{6cm}{0.4pt}
    
    \vspace{0.8cm}
    
    \item Word: \rule{6cm}{0.4pt}
    
    \vspace{0.8cm}
    
    \item Word: \rule{6cm}{0.4pt}
\end{enumerate}

\newpage

\section{Spaced Repetition Review}
\textit{These words appeared in previous sets. Complete the exercises to reinforce long-term retention.}

\begin{reviewbox}
\textbf{Review Words:} jeopardize (Set 1), withstand (Set 1), meddling (Set 1), ominous (Set 2), shrewd (Set 2)
\end{reviewbox}

\vspace{0.3cm}

\subsection*{Part A: Fill in the blanks}
\textit{Fill in the blanks with the correct review word:}

\begin{enumerate}
    \item The dark clouds and distant thunder were an \rule{3cm}{0.4pt} sign of the coming storm.
    
    \item Her constant \rule{3cm}{0.4pt} in other people's affairs made her very unpopular.
    
    \item A \rule{3cm}{0.4pt} businessman knows when to invest and when to hold back.
    
    \item Skipping your medication could \rule{3cm}{0.4pt} your recovery.
    
    \item The ancient walls were built to \rule{3cm}{0.4pt} enemy attacks.
\end{enumerate}

\vspace{0.3cm}

\subsection*{Part B: Similar words}
\textit{Which Set 3 words are SIMILAR in meaning?}

\begin{enumerate}
    \item \textit{ominous} (Set 2) is similar to \rule{3cm}{0.4pt} (Set 3) — both suggest something bad will happen.
    
    \item \textit{shrewd} (Set 2) is similar to \rule{3cm}{0.4pt} (Set 3) — both describe clever thinking.
    
    \item \textit{jeopardize} (Set 1) means to put at risk. A word with similar meaning from Set 3 describing a risky situation: \rule{3cm}{0.4pt}
\end{enumerate}

\newpage

% ============================================================
% HARD SECTION
% ============================================================

\begin{center}
\begin{tcolorbox}[colback=red!5!white, colframe=hardred, width=0.95\textwidth, arc=3mm, boxrule=1.5pt]
\begin{center}
{\Large\textbf{--- HARD EXERCISES ---}}\\[0.2cm]
{\large\textit{Production \& Analysis}}\\[0.3cm]
\textbf{Exercises 10-14} require production, analysis, and creative application.\\These are the most challenging exercises.
\end{center}
\end{tcolorbox}
\end{center}

\vspace{0.5cm}

\section{Trap Sentences — Spot the Error}
\textit{Each sentence contains ONE vocabulary error (wrong word, wrong form, or misused collocation). Find and correct it.}

\vspace{0.3cm}

\begin{enumerate}
    \item The police ceased the suspect's illegal weapons during the raid.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
    
    \vspace{0.2cm}
    
    \item He showed a brazing disregard for the safety rules, putting everyone at risk.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
    
    \vspace{0.2cm}
    
    \item She has a mischievious smile that always makes people suspicious of her intentions.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
    
    \vspace{0.2cm}
    
    \item Many small businesses have fallen on the wayside due to the economic crisis.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
    
    \vspace{0.2cm}
    
    \item The news of the scandal hastened her departure, therefore ending her political career.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
    
    \vspace{0.2cm}
    
    \item The crowd scattered together when they heard the alarm.
    
    Error: \rule{3cm}{0.4pt} → Correction: \rule{3cm}{0.4pt}
    
    Explanation: \rule{12cm}{0.4pt}
\end{enumerate}

\newpage

\section{Error Correction — Full Paragraph}
\textit{The following paragraph contains 8 errors related to Set 3 vocabulary (spelling, word choice, or usage). Find and underline each error, then write the correction below.}

\vspace{0.3cm}

\begin{tcolorbox}[colback=gray!10, colframe=gray!50]
The old mansion had a hidious appearance that sickened visitors. Dark clouds were looming over the threshold, creating an ominious atmosphere. The children, being michievous, decided to explore anyway. They had an uncanning feeling about the place, but their eager curiosity won over their fear. Inside, the bustlng sounds of their footsteps echoed through empty halls. When a door suddenly slammed shut, chaos ensured. "Let's scatter!" shouted the bravest one. "We need to get out save and sound!"
\end{tcolorbox}

\vspace{0.3cm}

\textbf{Corrections:}

\begin{enumerate}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
    \item \rule{4.75cm}{0.4pt} → \rule{4.75cm}{0.4pt}
\end{enumerate}

\vspace{0.5cm}

\section{Translation — Portuguese to English}
\textit{Translate the following sentences from Portuguese to English, using the appropriate Set 3 vocabulary words.}

\vspace{0.3cm}

\begin{enumerate}
    \item Ele é astuto como uma raposa — nunca confie nele completamente.
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.2cm}
    
    \item A situação parecia arriscada, mas chegamos sãos e salvos.
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.2cm}
    
    \item Ela teve um pressentimento ruim de que algo terrível iria acontecer.
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.2cm}
    
    \item O bebê precisa trocar a fralda — está chorando há horas.
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.2cm}
    
    \item Essas alegações são absolutamente absurdas — não faz sentido nenhum!
    
    \rule{\textwidth}{0.4pt}
    
    \vspace{0.2cm}
    
    \item Os soldados agarraram o prisioneiro antes que ele pudesse escapar.
    
    \rule{\textwidth}{0.4pt}
\end{enumerate}

\newpage

\section{Common Confusion Pairs}
\textit{Choose the correct word for each sentence. Both options are real words, but only one fits the context.}

\vspace{0.3cm}

\begin{enumerate}
    \item The police \rule{2cm}{0.4pt} the illegal shipment at the border.
    \begin{enumerate}[label=\alph*)]
        \item ceased
        \item seized
    \end{enumerate}
    
    \item After the announcement, chaos \rule{2cm}{0.4pt}.
    \begin{enumerate}[label=\alph*)]
        \item ensured
        \item ensued
    \end{enumerate}
    
    \item The situation looks rather \rule{2cm}{0.4pt} — I'm not sure we should proceed.
    \begin{enumerate}[label=\alph*)]
        \item dicy
        \item dicey
    \end{enumerate}
    
    \item She showed a \rule{2cm}{0.4pt} disregard for the rules.
    \begin{enumerate}[label=\alph*)]
        \item brazen
        \item brazing
    \end{enumerate}
    
    \item The \rule{2cm}{0.4pt} of the rainforest is home to many birds.
    \begin{enumerate}[label=\alph*)]
        \item canopy
        \item canape
    \end{enumerate}
    
    \item I prefer \rule{2cm}{0.4pt} breakfast items like eggs and bacon.
    \begin{enumerate}[label=\alph*)]
        \item savory
        \item savvy
    \end{enumerate}
    
    \item Regular exercise improves blood flow, \rule{2cm}{0.4pt} reducing the risk of heart disease.
    \begin{enumerate}[label=\alph*)]
        \item therefore
        \item thereby
    \end{enumerate}
    
    \item The children were being quite \rule{2cm}{0.4pt}, hiding their parents' keys.
    \begin{enumerate}[label=\alph*)]
        \item mischievous
        \item mischievious
    \end{enumerate}
\end{enumerate}

\newpage

\section{Use It or Lose It — Production Prompts}
\textit{Write original sentences or short paragraphs using the vocabulary words as indicated. Be creative!}

\vspace{0.3cm}

\subsection*{Part A: Single-Word Prompts}
\textit{Write one original sentence for each word:}

\begin{enumerate}
    \item \textbf{loom} (verb — something threatening):
    
    \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
    
    \item \textbf{threshold} (noun — a starting point or limit):
    
    \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
    
    \item \textbf{thereby} (adverb — connecting cause and effect):
    
    \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
    
    \item \textbf{unquenchable} (adjective — describing desire or thirst):
    
    \rule{\textwidth}{0.4pt}
    
    \rule{\textwidth}{0.4pt}
\end{enumerate}

\vspace{0.3cm}

\subsection*{Part B: Mini-Story Prompt}
\textit{Write a short paragraph (4-6 sentences) about a SCARY EXPERIENCE using at least 6 words from Set 3. Underline each vocabulary word you use.}

\vspace{0.2cm}

\textit{Suggested words: foreboding, loom, uncanny, hideous, fierce, scatter, seized, ensued, safe and sound}

\vspace{0.3cm}

\begin{enumerate}
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
\end{enumerate}

\vspace{0.3cm}

\subsection*{Part C: Dialogue Creation}
\textit{Write a short dialogue (4-6 exchanges) between two people in a BUSTLING CITY using at least 4 words from Set 3. Indicate the words used.}

\vspace{0.2cm}

\textit{Suggested words: bustling, eager, halt, nuisance, grip, scatter, uptight, dicey}

\vspace{0.3cm}

\begin{enumerate}
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
        
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
    
    \item[]
    \rule{\textwidth}{0.75pt}
\end{enumerate}

\newpage

% ============================================================
% QUICK REFERENCE PAGE (TEARABLE)
% ============================================================

\newpage
\pagestyle{empty}

\begin{center}
    {\Huge\bfseries Quick Reference}\\[0.3cm]
    {\Large Vocabulary Practice Set 3 — 40 Words}\\[0.2cm]
    \rule{\textwidth}{0.4pt}\\[0.2cm]
    {\small \textit{Tear these pages out for easy reference during exercises}}\\[0.1cm]
    \textit{Frequency: [H] High | [M] Medium | [L] Low}\\
    \textit{Register: [F] Formal | [C] Casual | [Lit] Literary | [!] Disapproving}
\end{center}

\vspace{0.3cm}

\begin{small}
\begin{longtable}{|p{2.8cm}|p{1cm}|p{1.2cm}|p{7.5cm}|}
\hline
\textbf{Word} & \textbf{Freq} & \textbf{Reg} & \textbf{Core Meaning} \\
\hline
\endfirsthead
\hline
\textbf{Word} & \textbf{Freq} & \textbf{Reg} & \textbf{Core Meaning} \\
\hline
\endhead
\hline
\endfoot

sicken & M & F & to disgust; cause shock/anger \\
\hline
insidious & M & F/Lit & spreading harm gradually, unnoticed \\
\hline
ensued & M & F & happened next (as a result) \\
\hline
diaper & H & C & baby's absorbent garment (AmE: diaper, BrE: nappy) \\
\hline
wayside & M & F & roadside; \textit{fall by the wayside} = fail/be neglected \\
\hline
brazen & M & ! & shamelessly bold; without guilt \\
\hline
ruffled & M & C & disturbed; decorated with frills \\
\hline
dizzy & H & C & feeling like spinning; overwhelmed \\
\hline
preposterous & M & F & absurdly ridiculous \\
\hline
hasten & M & F/Lit & hurry; speed up something \\
\hline
loom & M & F/Lit & appear threatening; seem imminent \\
\hline
tossed & H & C & threw lightly; moved restlessly \\
\hline
dicey & M & C & risky; uncertain (BrE slang) \\
\hline
foreboding & M & F/Lit & sense of coming danger \\
\hline
mischievous & H & C & playfully naughty \\
\hline
seized & H & F/C & grabbed forcefully; captured \\
\hline
canopy & M & F & covering (bed/trees); treetop layer \\
\hline
sass & M & C & rude backtalk; spirited attitude \\
\hline
halt & H & F & stop completely \\
\hline
nuisance & H & C/F & annoying person/thing \\
\hline
uncanny & M & F & strangely mysterious; eerily accurate \\
\hline
grievous & M & F & very serious (harm, error) \\
\hline
grin & H & C & wide smile showing teeth \\
\hline
savory & H & C & salty/spicy (not sweet) \\
\hline
fiendish & M & F/Lit & extremely cruel; devilishly difficult \\
\hline
unquenchable & L & F/Lit & impossible to satisfy \\
\hline
thereby & M & F & by that means; as a result \\
\hline
cunning & M & F/! & cleverly deceitful; crafty \\
\hline
lucky break & M & C & unexpected fortunate chance \\
\hline
bustling & H & C/F & full of busy activity \\
\hline
uptight & M & C & anxious; rigidly conventional \\
\hline
eager & H & C/F & enthusiastically wanting \\
\hline
threshold & H & F & doorway; starting point; limit \\
\hline
grip & H & C/F & firm hold; control; grasp \\
\hline
fierce & H & C/F & aggressively intense; violent \\
\hline
scatter & H & C/F & throw in many directions; disperse \\
\hline
hideous & M & C & extremely ugly; horrifying \\
\hline
safe and sound & H & C & completely unharmed \\
\hline
scum & M & !/C & surface layer; despicable person (strong insult) \\
\hline
twisted mind & M & ! & mentally disturbed/perverted thinking \\
\hline
\end{longtable}
\end{small}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.95\textwidth}{
\textbf{Review Words from Previous Sets} (5 words for spaced repetition):\\[0.1cm]
\textbf{Set 1:} \textit{jeopardize, withstand, meddling} \quad \textbf{Set 2:} \textit{ominous, shrewd}
}}
\end{center}

% ============================================================
% NOTES PAGES (RULED)
% ============================================================

\newpage

\section*{Personal Notes}

\textit{Use these pages to write down additional examples, mnemonics, or personal associations with the vocabulary words.}

\vspace{0.5cm}

\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}\\[0.5cm]
\noindent\rule{\textwidth}{0.2pt}

\end{document}

\end{document}
