\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{array}
\usepackage{longtable}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{English Vocabulary Practice}
\rhead{COMPREHENSIVE REVIEW}
\cfoot{\thepage}

% Section formatting
\titleformat{\section}
{\Large\bfseries\color{blue!70!black}}
{\thesection}{1em}{}

\titleformat{\subsection}
{\large\bfseries\color{blue!50!black}}
{\thesubsection}{1em}{}

% Custom colors
\definecolor{dragonball}{RGB}{255, 140, 0}
\definecolor{f1red}{RGB}{200, 16, 46}
\definecolor{peaky}{RGB}{40, 40, 40}
\definecolor{idiomcolor}{RGB}{75, 0, 130}

\begin{document}

\begin{center}
    {\Huge\bfseries Vocabulary Practice Exercises}\\[0.5cm]
    {\Large Comprehensive Review — Practice Set 1}\\[0.5cm]
    \rule{\textwidth}{0.4pt}\\[0.3cm]
    {\large 24 Words • 8 Exercise Types • Media Sources: Dragon Ball Z, F1, Peaky Blinders}\\[0.2cm]
    \today
\end{center}

\vspace{0.5cm}

\section*{Vocabulary Overview}

\textit{This practice set covers all vocabulary words learned so far. Words are organized by source media and word type.}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{\color{dragonball}Dragon Ball Z} & feistiest, resemblance, outstanding, foe, knack, ridge, search your feelings, half-baked, negate, meddling, jeopardize, withstand, pampered, pay through the nose, stubborn \\
\hline
\textbf{\color{f1red}F1} & steer \\
\hline
\textbf{\color{peaky}Peaky Blinders} & turn a blind eye to, sell someone to someone, parley, on the back foot \\
\hline
\end{tabularx}
\end{center}

\vspace{0.3cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Adjectives} & feistiest, outstanding, pampered, stubborn, half-baked \\
\hline
\textbf{Nouns} & resemblance, foe, knack, ridge, meddling, devastation \\
\hline
\textbf{Verbs} & negate, jeopardize, withstand, steer, parley \\
\hline
\textbf{Idioms \& Expressions} & search your feelings, pay through the nose, turn a blind eye to, sell someone to someone, on the back foot \\
\hline
\end{tabularx}
\end{center}

\newpage

% ============================================================
\section{Exercise 1: Definitions — Match the Word}

\textit{Match each definition (1-12) with the correct word from the word bank below.}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank A}\\[0.2cm]
feistiest \quad resemblance \quad foe \quad knack \quad ridge \quad pampered \quad \\
negate \quad jeopardize \quad withstand \quad stubborn \quad meddling \quad outstanding
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item A special skill or talent, often natural and hard to teach: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item To put something in danger; to risk losing or damaging: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item The state of looking like or being similar to someone/something: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Treated with excessive care; indulged or spoiled: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item To remain undamaged by; to resist or endure successfully: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item An enemy or opponent, especially in battle or conflict: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item The superlative form meaning ``most spirited'' or ``most bold'': \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Interfering in matters that don't concern you: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Extremely good; excellent or superior: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Refusing to change opinion; determined not to give in: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item To deny or make ineffective; to nullify: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item A long, narrow elevated area (mountain top or raised line): \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 2: Idioms \& Expressions — Fill in the Blanks}

\textit{Complete each sentence with the correct idiom or expression from the box.}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Idiom Bank}\\[0.2cm]
search your feelings \quad pay through the nose \quad turn a blind eye to \\
sell someone to someone \quad on the back foot \quad half-baked
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item The manager tried to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ me \_\_\_\_\_\_\_\_\_\_ the hiring committee by highlighting all my achievements.
    
    \item After the scandal broke, the politician found himself \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_, constantly defending his past decisions.
    
    \item I know you're scared, but \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ — deep down, you know this is the right choice.
    
    \item The authorities have been accused of \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ corruption for years.
    
    \item If you book the hotel at the last minute, you'll \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ for it.
    
    \item Your business plan sounds \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ — you haven't done enough research yet.
\end{enumerate}

\vspace{1cm}

% ============================================================
\section{Exercise 3: Word Forms — Complete the Table}

\textit{Fill in the missing word forms. Some cells may have ``---'' if no form exists.}

\vspace{0.5cm}

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|X|X|X|}
\hline
\textbf{Base Word} & \textbf{Noun} & \textbf{Verb} & \textbf{Adjective} & \textbf{Adverb} \\
\hline
\textbf{feisty} & feistiness & --- & feisty, feistier, \_\_\_\_\_\_\_ & \_\_\_\_\_\_\_ \\
\hline
\textbf{jeopardize} & \_\_\_\_\_\_\_ & jeopardize & --- & --- \\
\hline
\textbf{meddle} & \_\_\_\_\_\_\_, meddler & meddle & \_\_\_\_\_\_\_ & --- \\
\hline
\textbf{negate} & \_\_\_\_\_\_\_ & negate & negative & \_\_\_\_\_\_\_ \\
\hline
\textbf{stubborn} & \_\_\_\_\_\_\_ & --- & stubborn & \_\_\_\_\_\_\_ \\
\hline
\textbf{pamper} & \_\_\_\_\_\_\_ & pamper & \_\_\_\_\_\_\_ & --- \\
\hline
\textbf{withstand} & --- & withstand, \_\_\_\_\_\_\_ (past) & --- & --- \\
\hline
\textbf{steer} & \_\_\_\_\_\_\_ & steer & --- & --- \\
\hline
\end{tabularx}
\end{center}

\newpage

% ============================================================
\section{Exercise 4: Multiple Choice — Choose the Best Answer}

\textit{Circle the letter of the best answer for each question.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item The word ``outstanding'' can mean:
    \begin{enumerate}[label=\Alph*)]
        \item Only ``excellent'' or ``superior''
        \item Only ``not yet paid or resolved''
        \item Both ``excellent'' and ``pending/unpaid''
        \item Neither of the above
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item Which sentence uses ``foe'' correctly?
    \begin{enumerate}[label=\Alph*)]
        \item He was a foe of vegetables, preferring only meat.
        \item The hero faced his greatest foe in the final battle.
        \item She made a foe for chocolate cake.
        \item The foe weather ruined our picnic.
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item ``She has a knack for learning languages.'' This means she:
    \begin{enumerate}[label=\Alph*)]
        \item Struggles with languages
        \item Has a natural talent for languages
        \item Dislikes learning languages
        \item Is forced to learn languages
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item What is the past tense of ``withstand''?
    \begin{enumerate}[label=\Alph*)]
        \item withstanded
        \item withstood
        \item withstand
        \item withstanding
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item ``Turn a blind eye to'' is closest in meaning to:
    \begin{enumerate}[label=\Alph*)]
        \item Look carefully at something
        \item Deliberately ignore something wrong
        \item Have poor vision
        \item Be surprised by something
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item If a plan is ``half-baked,'' it is:
    \begin{enumerate}[label=\Alph*)]
        \item Perfectly prepared
        \item Incomplete or poorly thought out
        \item Made with half the ingredients
        \item Cooking in the oven
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item ``Parley'' is most commonly used in which context?
    \begin{enumerate}[label=\Alph*)]
        \item Cooking and baking
        \item Negotiations between enemies
        \item Sports commentary
        \item Fashion design
    \end{enumerate}
    
    \vspace{0.3cm}
    
    \item A ``ridge'' can refer to all EXCEPT:
    \begin{enumerate}[label=\Alph*)]
        \item The top of a mountain chain
        \item Raised lines on fingerprints
        \item A valley between two hills
        \item A weather pattern (high pressure)
    \end{enumerate}
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 5: Sentence Completion — Use the Word in Context}

\textit{Complete each sentence with the appropriate word. Use the correct form (tense, plural, etc.).}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank}\\[0.2cm]
resemble \quad steer \quad jeopardize \quad pamper \quad negate \quad \\
withstand \quad meddle \quad stubborn \quad feisty \quad outstanding
}}
\end{center}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item The twins bear a striking \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ to each other — it's hard to tell them apart.
    
    \item Don't let one bad decision \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ all the hard work you've done.
    
    \item Despite his small size, the puppy was the \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ of the litter, always barking at bigger dogs.
    
    \item The captain carefully \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ the ship through the narrow channel.
    
    \item Her new evidence completely \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ his alibi — he couldn't have been there.
    
    \item After the stressful week, she decided to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ herself with a spa day.
    
    \item The old bridge was designed to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ heavy traffic and harsh weather.
    
    \item Stop \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ in my business — I can make my own decisions!
    
    \item He's so \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ that he won't change his mind even when he's clearly wrong.
    
    \item She received an award for her \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ contribution to the field of medicine.
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 6: Synonyms \& Antonyms}

\subsection*{Part A: Match the Synonyms}

\textit{Draw a line connecting each word on the left with its synonym on the right.}

\vspace{0.3cm}

\begin{multicols}{2}
\begin{enumerate}[leftmargin=1cm]
    \item foe
    \item resemblance
    \item jeopardize
    \item stubborn
    \item outstanding
    \item knack
\end{enumerate}

\columnbreak

\begin{enumerate}[label=\Alph*), leftmargin=1cm]
    \item excellent
    \item similarity
    \item endanger
    \item enemy
    \item obstinate
    \item talent
\end{enumerate}
\end{multicols}

\vspace{0.5cm}

\subsection*{Part B: Write the Antonym}

\textit{Write an antonym (opposite) for each word.}

\begin{enumerate}[leftmargin=2cm]
    \item foe $\rightarrow$ \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \item pampered $\rightarrow$ \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \item outstanding (meaning: excellent) $\rightarrow$ \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \item half-baked $\rightarrow$ \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    \item stubborn $\rightarrow$ \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{enumerate}

\vspace{1cm}

% ============================================================
\section{Exercise 7: Error Correction}

\textit{Each sentence contains one vocabulary error. Find and correct it.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item She has a nack for playing the piano — she never took lessons! \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item The building withstanded the earthquake without major damage. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item He paid through the eye for those concert tickets. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item The company turned the blind eye to safety violations. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item After the bad review, the restaurant was at the back foot. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Your proposal sounds half-backed — you need more data. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item The hero defeated his greatest foe in battle. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (No error — this sentence is correct!)
    
    \item That metaling neighbor is always asking about our personal life. \\
    \textit{Correction:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 8: Collocations — Choose the Right Partner}

\textit{Circle the word that best completes each collocation.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item bear a (strong / heavy / big) resemblance
    
    \item (bitter / sour / angry) foe
    
    \item have a (knack / knock / nack) for something
    
    \item (mountain / field / ocean) ridge
    
    \item withstand (pressure / opinion / color)
    
    \item (bureaucratic / democratic / automatic) meddling
    
    \item jeopardize someone's (safety / color / taste)
    
    \item (pampered / hammered / gathered) lifestyle
    
    \item stubborn as a (mule / mouse / monkey)
    
    \item put someone on the (back / front / side) foot
\end{enumerate}

\vspace{1cm}

% ============================================================
\section{Exercise 9: Translation Practice}

\textit{Translate these sentences from Portuguese to English using the vocabulary words studied.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item Ele é um garoto mimado que nunca precisou trabalhar. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item O prédio foi projetado para resistir a terremotos. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item As autoridades fizeram vista grossa para a corrupção. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Pagamos caro demais por ingressos de última hora. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item O gol cedo os colocou na defensiva. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \item Ela tem um jeito para resolver problemas rapidamente. \\
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 10: Context Clues — Guess the Word}

\textit{Read each mini-context and guess which vocabulary word fits best.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item \textbf{Context:} The small dog kept barking at the German Shepherd, showing no fear despite being one-tenth its size. Everyone laughed at how spirited and bold the little puppy was.
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (adjective, superlative form)
    
    \vspace{0.3cm}
    
    \item \textbf{Context:} ``I've explained this a thousand times,'' she sighed, ``but he refuses to accept he might be wrong. He won't budge an inch.''
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item \textbf{Context:} Before the big battle, the generals from both armies met in the middle of the field to discuss terms and try to avoid bloodshed.
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (verb, old-fashioned)
    
    \vspace{0.3cm}
    
    \item \textbf{Context:} The racing driver expertly controlled the car through the tight corners, keeping perfect command of the vehicle's direction at high speeds.
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (verb)
    
    \vspace{0.3cm}
    
    \item \textbf{Context:} ``People always say I look just like my grandmother when she was young. We have the same eyes, the same smile, even the same way of walking.''
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (noun)
    
    \vspace{0.3cm}
    
    \item \textbf{Context:} The startup presented their business plan, but the investors found it incomplete — they hadn't considered costs, competition, or even their target market.
    
    \textit{Word:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (idiom, adjective)
\end{enumerate}

\newpage

% ============================================================
\section{Exercise 11: Creative Writing — Use the Words}

\textit{Write a short paragraph (5-8 sentences) using at least 6 of the vocabulary words from this practice set. You can write about any topic you like: a story, a description, an opinion, etc.}

\vspace{0.5cm}

\textbf{Words to choose from:} feistiest, resemblance, outstanding, foe, knack, ridge, pampered, stubborn, negate, jeopardize, withstand, meddling, steer, parley, half-baked, on the back foot, turn a blind eye to, pay through the nose, search your feelings, sell someone to someone

\vspace{0.5cm}

\noindent\rule{\textwidth}{0.4pt}

\vspace{7cm}

\noindent\rule{\textwidth}{0.4pt}

\vspace{1cm}

% ============================================================
\section{Exercise 12: Word Origins — Etymology Matching}

\textit{Match each word with its origin/etymology.}

\vspace{0.5cm}

\begin{multicols}{2}
\textbf{Words:}
\begin{enumerate}[leftmargin=1cm]
    \item ridge
    \item knack
    \item parley
    \item negate
    \item foe
\end{enumerate}

\columnbreak

\textbf{Origins:}
\begin{enumerate}[label=\Alph*), leftmargin=1cm]
    \item From Old English ``fāh'' (hostile)
    \item From French ``parler'' (to speak)
    \item From Latin ``negare'' (to deny)
    \item From Old English ``hrycg'' (back, spine)
    \item From an imitative word for a sharp sound/trick
\end{enumerate}
\end{multicols}

\newpage

% ============================================================
\section{Exercise 13: Sentence Transformation}

\textit{Rewrite each sentence using the word in brackets without changing the meaning.}

\vspace{0.5cm}

\begin{enumerate}[leftmargin=2cm]
    \item The team was in a difficult, defensive position after the early mistake. (BACK FOOT)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item She has a natural talent for cooking. (KNACK)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item The officials deliberately ignored the corruption happening under their noses. (BLIND EYE)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item The child was spoiled and given too much attention by his parents. (PAMPERED)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item Don't risk your career over one bad decision. (JEOPARDIZE)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
    
    \vspace{0.3cm}
    
    \item We paid way too much for these hotel rooms. (NOSE)
    
    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{enumerate}

\vspace{1cm}

% ============================================================
\section{Exercise 14: Fill the Story}

\textit{Complete this short story using words from the box. Each word is used once.}

\vspace{0.3cm}

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{Word Bank}\\[0.2cm]
feistiest \quad foe \quad resemblance \quad stubborn \quad withstood \quad \\
pampered \quad meddling \quad jeopardized \quad outstanding \quad steered
}}
\end{center}

\vspace{0.5cm}

Marcus was the (1) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ kid in his class — small but fierce, never backing down from anyone. His (2) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ nature sometimes got him into trouble, but it also earned him respect.

At home, his younger brother Leo was the opposite: a (3) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ child who had never faced real challenges. Despite their differences, they shared a striking (4) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ — the same bright eyes and mischievous smile.

One day, Marcus met his greatest (5) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ on the basketball court: a tall player named Derek. The game was intense, but Marcus (6) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ the pressure and delivered an (7) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ performance.

Meanwhile, their (8) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ neighbor Mrs. Chen almost (9) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ the victory by calling the police about the noise! Luckily, Marcus (10) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ the situation away from disaster by charming her with his smile.

\vspace{2cm}

\begin{center}
    \rule{0.5\textwidth}{0.4pt}\\
    \vspace{0.3cm}
    {\large\textbf{End of Exercises}}\\
    \vspace{0.2cm}
    \textit{Check your answers with the answer key}
\end{center}

\end{document}
